Outbreak Threshold Detection

### 2023-08-16 notebooks/Julia/simulation-detection.qmd
Rename sigma vars for clarity

μ = 1
beta = 1000
σ = 365/8
γ = 365/5
ε = 100
p = (beta, σ, γ, μ, ε)
```

@@

infec_rate(u, p, t) = p[2] * u[2]   # σ * E
function infec_affect!(integrator)
    integrator.u[2] -= 1         # E -> E - 1
    integrator.u[3] += 1         # I -> I + 1
    nothing
end
infec_jump = ConstantRateJump(infec_rate, infec_affect!)

>>>>

μ = 1
beta = 1000
sigma = 365/8
γ = 365/5
ε = 100
p = (beta, sigma, γ, μ, ε)
```

@@

infec_rate(u, p, t) = p[2] * u[2]   # sigma * E
function infec_affect!(integrator)
    integrator.u[2] -= 1         # E -> E - 1
    integrator.u[3] += 1         # I -> I + 1
    nothing
end
infec_jump = ConstantRateJump(infec_rate, infec_affect!)
